---
title: "HW2 Telemarketing"
author: "Elise Gordon - Worked with Michael Kalmus during class"
date: "11/8/2020"
output:
  html_document:
    toc: true
    theme: readable
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Downloading and Prepping the Data

```{r}
#Downloading and Prepping the Data
tele <- read.csv("tele.csv", stringsAsFactors = TRUE)
summary(tele)
```

```{r}
#We are deleting the "duration" variable because it is an after the fact measurement. We only should be using variables that we know before the call
tele$duration <- NULL

# Deleting the column X
tele$X <- NULL

# Changing pdays to a dummy and deleting pdays
tele$pdaysdummy <- ifelse(tele$pdays == 999, 0, 1)
tele$pdays <- NULL

str(tele)
```

## Getting Data Ready for Analysis

```{r}
#Optional simplifying of data
tele$job <- NULL
tele$month <- NULL
tele$day_of_week <- NULL
```

```{r}
# Using model.matrix to convert all the factors to dummy variables
# We are converting all of the factors into dummy variables as the input into ANN has to be numeric
telemm <- as.data.frame(model.matrix(~.-1,tele)) 
str(telemm)

# Randomize the rows in the data (shuffling the rows)
set.seed(12345)
tele_random <- telemm[sample(nrow(telemm)),]

#Normalize the data
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# we are going to normalize everything 
tele_norm <- as.data.frame(lapply(tele_random, normalize))
```
```{r}
summary(tele_norm)
```

## Getting Train and Test Samples

```{r}
# Selects 10000 random rows for test data
set.seed(12345)
test_set <- sample(1:nrow(tele_norm), 10000) 
# Depending on R-version and computer, different rows may be selected. 
# If that happens, results are different. 

# Create a train set and test set
#First the predictors - all columns except the yyes column
tele_train <- tele_norm[-test_set, ]
tele_test <- tele_norm[test_set, ]
```

> Now you are ready to build your ANN model. Feel free to modify the data load, cleaning and preparation code above as per your preference.

## Logistic Regression Model

We will build a simple logistic regression model and use that to show how to do prediction and model evaluation.

### Simple Model Building

```{r}
#note: we build the model using the training set
simplemodel <- glm(yyes ~ ., data = tele_train, family = binomial(link = "logit"))
```

```{r}
stepmodel <- step(simplemodel, direction = "backward")
```

### Prediction based on Step Model

```{r}
pred_step <- predict(stepmodel, tele_test, type = "response")
summary(pred_step)
#pred_cat <- ifelse(pred_step >= 0.5, 1, 0)
pred_cat <- ifelse(pred_step >= 0.3, 1, 0)
table(pred_cat)
300 / 9700
table(tele_train$yyes)
3491 / 27697
```

Comparing these results, we can say that 0.5 is not a good threshold and must be lowered. 

### Evaluation of Model

Now we create a confusion matrix. This shows us if our binary predictions were good or not. 

```{r}
library(caret)
confusionMatrix(factor(pred_cat), factor(tele_test$yyes), positive = "1")
```
Accuracy represents how many we are getting right (true positives and true negatives). Note that our accuracy of ~89% is not really good.

True positive (TP): 462

True negative (TN): 8422

False positive (FP): 429

False negative (FN):  687


## Build ANN model to predict yyes, predict test data and build confusion matrix 
```{r}
# Load relevant libraries
library(neuralnet)

# simple ANN with only a single hidden neuron
tele_model <- neuralnet(formula = yyes ~ .,
                              data = tele_train)

summary(tele_model)
```

```{r}
#Plot the NN
plot(tele_model)
```

```{r}
# obtain model results
model_results <- compute(tele_model, tele_test[,-29])

# obtain predicted strength values
predicted_yyes <- model_results$net.result

summary(predicted_yyes)
```

```{r}
#Set threshold 
pred_cat_nn <- ifelse(predicted_yyes >= 0.5, 1, 0)
#Create confusion matrix
confusionMatrix(factor(pred_cat_nn), factor(tele_test$yyes), positive = "1")
```
True Positive: 229

True Negative: 8772

False Positive: 128

False Negative: 871

```{r}
#validate accuracy
(8772 + 229) / (8772 + 229 + 128 + 871)
```

I would rather use the ANN model for this prediction for several reasons. Not only was it more accurate than the linear regression model, but ANN is usually a better model when there are a lot of variables. In this case, there are a lot of different potential factors influencing the call success, so the linear regression model might confound certain variables that aren't actually influential. 
